---
title: "SeminR Visualization tool"
author: "André Calero Valdez"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(seminr)
library(DiagrammeR)
library(glue)
source("GraphGen/seminrvis.R")

```


# Setup a Model that works both in CB and PLS

## Setup Measurement model 

We choose a model that also uses interactions, because these are hard to visualize. The result of the model is not important here.

```{r measurements, class.source = 'fold-show'}
measurements <- constructs(
  reflective("Image",        multi_items("IMAG", 1:5)),
  reflective("Expectation",  multi_items("CUEX", 1:3)),
  reflective("Value",        multi_items("PERV", 1:2)),
  reflective("Satisfaction", multi_items("CUSA", 1:3)),
  interaction_term(iv = "Image", moderator = "Expectation", method = orthogonal),
  interaction_term(iv = "Image", moderator = "Value", method = product_indicator)
)

```

## Setup structural model


```{r structure, class.source = 'fold-show'}
# Create four relationships (two regressions) in one line!
structure <- relationships(
  paths(to = "Satisfaction",
        from = c("Image", "Expectation", "Value",
                 "Image*Expectation", "Image*Value"))
)
```


# Run the model

First we estimate the model using standard parameters.

```{r pls, class.source = 'fold-show'}
pls_model <- estimate_pls(data = mobi, measurements, structure)
pls_model %>% summary()
```

## Plotting the model

First we plot the model using default settings (for inspection).
Constructs are shown in black, and items in dimgray.


```{r pls_plot}
pls_model %>% plot_model() %>% grViz()
```


### Fine-Tuning the plot.

Currently, the plot needs manual fine-tuning.
E.g., length and width of constructs and items is guessed using `strwidth` and `strheight` in R.

Manually picked the longest item and construct text. 

```{r guess_heights}
ifontsize <- 9
iwidth <- strwidth('CUSA9', font = ifontsize, units = 'in') + 0.1
iheight <- strheight('CUSA9', font = ifontsize, units = 'in') + 0.1

cfontsize <- 12
cwidth <- strwidth('Image_x_Expectation', font = cfontsize, units = 'in') + 0.3
cheight <- strheight('Image_x_Expectation', font = cfontsize, units = 'in') + 0.3
```

Now we emulate a SMART-PLS plot (badly).

```{r pls_plot2}

pls_model %>% plot_model(
  # we can have a title
  title = "PLS-SEM Plot with interactions",
  
  # we can style the item appearance
  item_style = createItemStyle(
    fontsize = ifontsize, 
    width = iwidth, height = iheight, 
    color = "black", fill = "lightgoldenrodyellow"),
  
  # we can style the construct appearance
  construct_style = createConstructStyle(
    fontsize = cfontsize, 
    width = cwidth, height = cheight, 
    color = "black", fill = "lightcyan"),
  
  # we can style the outer weight edges
  outer_weight_style = createOuterWeightStyle(color = "dimgray"),
  
  # we can style the inner weight edges
  inner_weight_style = createInnerWeightStyle(color = "black", fontsize = 12)
  ) %>% 
  grViz()
```


# TODO

1. add adj r^2 in output (where?)
1. Currently arrow direction is not adjusted for when using refletive/formative models.
1. auto-detect optimal sizes
1.1 for ellipses as well
1. change width of edges to values
1. use bootstrapped models
2. show estimation type (composite, reflective, A, B)
3. CB Sem?

# Bootstrapped PLS

```{r bootstrap}
bs_model <- bootstrap_model(pls_model, nboot = 1000) 

bs_model %>% summary()
```


## Bootstrapped HTMT

```{r bootstrap_htmt, results='asis'}
options(knitr.kable.NA = '')

bs_model$HTMT_descriptives[1:6,7:12] %>% 
  as_tibble(rownames = "HTMT Table") %>% 
  knitr::kable(digits = 3)
```


# CBSEM

```{r cbsem}
# Put together reusable parts of your model to estimate CBSEM results
cbsem_model <- estimate_cbsem(data = mobi, measurements, structure)

cbsem_model %>% summary()
```

